\vspace{5em}On Evaluating Adversarial Robustness

### 2019-05-13 paper.tex
separate sanity tests for iterations and restarts

It is customary for defenses not to impose any computational bounds on an attacker (i.e., the above definitions of adversarial risk consider only the \emph{existence} of adversarial examples, and not the difficulty of finding them). We believe that restricting an adversary's computational power would only be interesting if we could base robustness on a cryptographic assumption (e.g., the model is robust under the assumption that the adversary cannot factor a product of large primes). We are not aware of any defense that achieves this. Stronger restrictions (e.g., the adversary is limited to attacks with $100$ iterations) are typically uninteresting in that they cannot be meaningfully enforced and there is usually no economic reason for an adversary not to spend a little more time to succeed.

@@

\begin{itemize}[leftmargin=*]
  \item \S\ref{sec:pleaseactuallythink} \textbf{Do not mindlessly follow this list}; make sure to still think about the evaluation.
\item \S\ref{sec:threatmodel} \textbf{State a precise threat model} that the defense is supposed to be effective under.
  \begin{itemize}[leftmargin=*]
  \item The threat model assumes the attacker knows how the defense works.
  \item The threat model states attacker's goals, knowledge and capabilities.
  \item For security-justified defenses, the threat model realistically models some adversary.
  \item For worst-case randomized defenses, the threat model captures the perturbation space.
  \item Think carefully and justify any $\ell_p$ bounds placed on the adversary.
  \end{itemize}
\item \S\ref{sec:adaptive} Perform \textbf{adaptive attacks} to give an upper bound of robustness.
  \begin{itemize}[leftmargin=*]
  \item The attacks are given access to the full defense, end-to-end.
  \item The loss function is changed as appropriate to cause misclassification.
  \item \S\ref{sec:whichattack} \textbf{Focus on the strongest attacks} for the threat model and defense considered.
  \end{itemize}
\item \S\ref{sec:releasecode} Release \textbf{pre-trained models and source code}.
  \begin{itemize}[leftmargin=*]
  \item Include a clear installation guide, including all dependencies.
  \item There is a one-line script which will classify an input example with the defense.
  \end{itemize}
\item \S\ref{sec:cleanaccuracy} Report \textbf{clean model accuracy} when not under attack.
  \begin{itemize}[leftmargin=*]
  \item For defenses that abstain or reject inputs, generate a ROC curve.
  \end{itemize}
\item \S\ref{sec:sanitycheck} Perform \textbf{basic sanity tests} on attack success rates.
  \begin{itemize}[leftmargin=*]
    \item Verify iterative attacks perform better than single-step attacks.
    \item Verify that iterative-attacks use sufficient iterations and random restarts to converge. 
    \item Verify increasing the perturbation budget strictly increases attack success rate.
    \item With ``high'' distortion, model accuracy should reach levels of random guessing.% or even drop to zero.
  \end{itemize}
\item \S\ref{sec:100success} Generate an \textbf{attack success rate vs. perturbation budget} curve.
  \begin{itemize}[leftmargin=*]
  \item Verify the x-axis extends so that attacks eventually reach 100\% success.
  \item For unbounded attacks, report distortion and not success rate.
  \end{itemize}
\item \S\ref{sec:whitebox} Verify \textbf{adaptive attacks} perform better than any other.
  \begin{itemize}[leftmargin=*]
  \item Compare success rate on a per-example basis, rather than averaged across the dataset.
  \item Evaluate against some combination of black-box, transfer, and random-noise attacks.
  \end{itemize}
\item \S\ref{sec:describeattacks} Describe the \textbf{attacks applied}, including all hyperparameters.

@@

\begin{itemize}[leftmargin=*]
\item \S\ref{sec:whichattack} Apply a \textbf{diverse set of attacks} (especially when training on one attack approach).
  \begin{itemize}[leftmargin=*]
  \item Do not blindly apply multiple (nearly-identical) attack approaches.
  \end{itemize}
\item \S\ref{sec:gradientfree} Try at least one \textbf{gradient-free attack} and one \textbf{hard-label attack}.
  \begin{itemize}[leftmargin=*]
  \item Try \cite{chen2017zoo,uesato2018adversarial,ilyas2018black,brendel2017decision}.
  \item Check that the gradient-free attacks succeed less often than gradient-based attacks.
  \item Carefully investigate attack hyperparameters that affect success rate.
  \end{itemize}
\item \S\ref{sec:transfer} Perform a \textbf{transferability attack} using a similar substitute model.
  \begin{itemize}[leftmargin=*]
    \item Select a substitute model as similar to the defended model as possible.
    \item Generate adversarial examples that are initially assigned high confidence.
    \item Check that the transfer attack succeeds less often than white-box attacks.
  \end{itemize}
\item \S\ref{sec:eot} For randomized defenses, properly \textbf{ensemble over randomness}.
  \begin{itemize}[leftmargin=*]
  \item Verify that attacks succeed if randomness is assigned to one fixed value.
  \item State any assumptions about adversary knowledge of randomness in the threat model.
  \end{itemize}
\item \S\ref{sec:bpda} For non-differentiable components, \textbf{apply differentiable techniques}.
  \begin{itemize}[leftmargin=*]
  \item Discuss why non-differentiable components were necessary.
  \item Verify attacks succeed on undefended model with those non-differentiable components.
  \item Consider applying BPDA~\citep{athalye2018obfuscated} if applicable.
  \end{itemize}
\item \S\ref{sec:converge} Verify that the \textbf{attacks have converged} under the selected hyperparameters.
  \begin{itemize}[leftmargin=*]
  \item Verify that doubling the number of iterations does not increase attack success rate nor significantly change the adversarial loss.
  \item Plot attack effectiveness versus the number of iterations.
  \item Run attacks with multiple random starting points and retain the best one.
  \item Explore different choices of the step size or other attack hyperparameters.
  \end{itemize}
\item \S\ref{sec:hyperparams} Carefully \textbf{investigate attack hyperparameters} and report those selected.
  \begin{itemize}[leftmargin=*]
  \item Start search for adversarial examples at a random offset. Try multiple random starting points for each input.
  \item Investigate if attack results are sensitive to any other hyperparameters.
  \end{itemize}
  \item \S\ref{sec:priorwork} \textbf{Compare against prior work} and explain important differences.
  \begin{itemize}[leftmargin=*]
  \item When contradicting prior work, clearly explain why differences occur.
  \item Attempt attacks that are similar to those that defeated previous similar defenses.
  \item When comparing against prior work, ensure it has not been broken.
  \end{itemize}
\item \S\ref{sec:generalrobustness} Test \textbf{broader threat models} when proposing general defenses. For images:
  \begin{itemize}[leftmargin=*]
  \item Apply rotations and translations \citep{engstrom2017rotation}.
  \item Apply common corruptions and perturbations \citep{hendrycks2018benchmarking}.
  \item Add Gaussian noise of increasingly large standard deviation \citep{ford2019adversarial}.
  \end{itemize}

@@

There are few reasonable threat models under which an attacker can
compute 100 iterations of gradient descent, but not 1000. As stated in~\cite{athalye2018obfuscated}, merely increasing the time it takes an adversary to find an adversarial example (e.g., from one second to ten seconds) does not constitute an increase in robustness.
%
Because the threat model must not constrain the approach an
attacker takes, it is worth evaluating against a strong attack
with many iterations of gradient descent, as well as many different random restarts (to avoid converging to sub-optimal local minima~\citep{madry2017towards,mosbach2018logit}).

@@

>>>>

It is customary for defenses not to impose any computational bounds on an attacker 
(i.e., the above definitions of adversarial risk consider only the \emph{existence} of adversarial 
examples, and not the difficulty of finding them). We believe that restricting an adversary's 
computational power could be interesting if we could make formal statements about the 
computational cost of finding adversarial examples (e.g., via a reduction to a concrete hardness 
assumption as is done in cryptography). We are not aware of any defense that currently achieves 
this. Stronger restrictions (e.g., the adversary is limited to attacks with $100$ iterations) are 
usually uninteresting in that they cannot be meaningfully enforced and there is often no 
economic reason for an adversary not to spend a little more time to succeed.

@@

\begin{itemize}[leftmargin=*]
  \item \S\ref{sec:pleaseactuallythink} \textbf{Do not mindlessly follow this list}; make sure to still think about the evaluation.
\item \S\ref{sec:threatmodel} \textbf{State a precise threat model} that the defense is supposed to be effective under.
  \begin{itemize}[leftmargin=*]
  \item The threat model assumes the attacker knows how the defense works.
  \item The threat model states attacker's goals, knowledge and capabilities.
  \item For security-justified defenses, the threat model realistically models some adversary.
  \item For worst-case randomized defenses, the threat model captures the perturbation space.
  \item Think carefully and justify any $\ell_p$ bounds placed on the adversary.
  \end{itemize}
\item \S\ref{sec:adaptive} Perform \textbf{adaptive attacks} to give an upper bound of robustness.
  \begin{itemize}[leftmargin=*]
  \item The attacks are given access to the full defense, end-to-end.
  \item The loss function is changed as appropriate to cause misclassification.
  \item \S\ref{sec:whichattack} \textbf{Focus on the strongest attacks} for the threat model and defense considered.
  \end{itemize}
\item \S\ref{sec:releasecode} Release \textbf{pre-trained models and source code}.
  \begin{itemize}[leftmargin=*]
  \item Include a clear installation guide, including all dependencies.
  \item There is a one-line script which will classify an input example with the defense.
  \end{itemize}
\item \S\ref{sec:cleanaccuracy} Report \textbf{clean model accuracy} when not under attack.
  \begin{itemize}[leftmargin=*]
  \item For defenses that abstain or reject inputs, generate a ROC curve.
  \end{itemize}
\item \S\ref{sec:sanitycheck} Perform \textbf{basic sanity tests} on attack success rates.
  \begin{itemize}[leftmargin=*]
    \item Verify iterative attacks perform better than single-step attacks.
    \item Verify that iterative-attacks use sufficient iterations to converge. 
    \item Verify that attacks use sufficient random restarts to avoid sub-optimal local minima.
    \item Verify increasing the perturbation budget strictly increases attack success rate.
    \item With ``high'' distortion, model accuracy should reach levels of random guessing.% or even drop to zero.
  \end{itemize}
\item \S\ref{sec:100success} Generate an \textbf{attack success rate vs. perturbation budget} curve.
  \begin{itemize}[leftmargin=*]
  \item Verify the x-axis extends so that attacks eventually reach 100\% success.
  \item For unbounded attacks, report distortion and not success rate.
  \end{itemize}
\item \S\ref{sec:whitebox} Verify \textbf{adaptive attacks} perform better than any other.
  \begin{itemize}[leftmargin=*]
  \item Compare success rate on a per-example basis, rather than averaged across the dataset.
  \item Evaluate against some combination of black-box, transfer, and random-noise attacks.
  \end{itemize}
\item \S\ref{sec:describeattacks} Describe the \textbf{attacks applied}, including all hyperparameters.

@@

\begin{itemize}[leftmargin=*]
\item \S\ref{sec:whichattack} Apply a \textbf{diverse set of attacks} (especially when training on one attack approach).
  \begin{itemize}[leftmargin=*]
  \item Do not blindly apply multiple (nearly-identical) attack approaches.
  \end{itemize}
\item \S\ref{sec:gradientfree} Try at least one \textbf{gradient-free attack} and one \textbf{hard-label attack}.
  \begin{itemize}[leftmargin=*]
  \item Try \cite{chen2017zoo,uesato2018adversarial,ilyas2018black,brendel2017decision}.
  \item Check that the gradient-free attacks succeed less often than gradient-based attacks.
  \item Carefully investigate attack hyperparameters that affect success rate.
  \end{itemize}
\item \S\ref{sec:transfer} Perform a \textbf{transferability attack} using a similar substitute model.
  \begin{itemize}[leftmargin=*]
    \item Select a substitute model as similar to the defended model as possible.
    \item Generate adversarial examples that are initially assigned high confidence.
    \item Check that the transfer attack succeeds less often than white-box attacks.
  \end{itemize}
\item \S\ref{sec:eot} For randomized defenses, properly \textbf{ensemble over randomness}.
  \begin{itemize}[leftmargin=*]
  \item Verify that attacks succeed if randomness is assigned to one fixed value.
  \item State any assumptions about adversary knowledge of randomness in the threat model.
  \end{itemize}
\item \S\ref{sec:bpda} For non-differentiable components, \textbf{apply differentiable techniques}.
  \begin{itemize}[leftmargin=*]
  \item Discuss why non-differentiable components were necessary.
  \item Verify attacks succeed on undefended model with those non-differentiable components.
  \item Consider applying BPDA~\citep{athalye2018obfuscated} if applicable.
  \end{itemize}
\item \S\ref{sec:converge} Verify that the \textbf{attacks have converged} under the selected hyperparameters.
  \begin{itemize}[leftmargin=*]
  \item Verify that doubling the number of iterations does not increase attack success rate nor significantly change the adversarial loss.
  \item Plot attack effectiveness versus the number of iterations.
  \item Run attacks with multiple random starting points and retain the best one.
  \item Explore different choices of the step size or other attack hyperparameters.
  \end{itemize}
\item \S\ref{sec:hyperparams} Carefully \textbf{investigate attack hyperparameters} and report those selected.
  \begin{itemize}[leftmargin=*]
  \item Start search for adversarial examples at a random offset. Try multiple random starting points for each input.
  \item As for the number of attack iterations, verify that increasing the number of random restarts does not affect the attack's success rate or the adversarial loss.
  \item Investigate if attack results are sensitive to any other hyperparameters.
  \end{itemize}
  \item \S\ref{sec:priorwork} \textbf{Compare against prior work} and explain important differences.
  \begin{itemize}[leftmargin=*]
  \item When contradicting prior work, clearly explain why differences occur.
  \item Attempt attacks that are similar to those that defeated previous similar defenses.
  \item When comparing against prior work, ensure it has not been broken.
  \end{itemize}
\item \S\ref{sec:generalrobustness} Test \textbf{broader threat models} when proposing general defenses. For images:
  \begin{itemize}[leftmargin=*]
  \item Apply rotations and translations \citep{engstrom2017rotation}.
  \item Apply common corruptions and perturbations \citep{hendrycks2018benchmarking}.
  \item Add Gaussian noise of increasingly large standard deviation \citep{ford2019adversarial}.
  \end{itemize}

@@

There are few reasonable threat models under which an attacker can
compute 100 iterations of gradient descent, but not 1000. Similarly, as stated 
in~\cite{athalye2018obfuscated}, increasing the time it takes an adversary to find an adversarial 
example from one second to ten seconds does typically not constitute an increase in robustness. 
Of course, if a future defense manages to provide strong (and preferably provable) lower bounds 
on the  computational cost of an attack, this might still be interesting if these lower bounds are 
prohibitively large (e.g., the attack requires at least $2^{30}$ gradient evaluations).
%
In general, because the threat model must not constrain the approach an
attacker takes, it is worth evaluating against a strong attack
with many iterations of gradient descent, as well as many different random restarts 
(to avoid converging to sub-optimal local minima~\citep{madry2017towards,mosbach2018logit}).

@@

As for verifying attack convergence, a good test would be to check that doubling the
number of random restarts (e.g., from $10$ to $20$) does not affect the attack's 
success rate and adversarial loss.
